Does Happiness Lead to Altruism: A review of US General Social Survey data

### 2023-03-15 outputs/paper/paper.qmd
Updated paper graphs

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Happiness vs Altruism"
#| label: fig-1

@@

  geom_line(data = happy_positive_data, aes(x = year, y = people, color = "Happiness")) +
  geom_line(data = directions_positive_data, aes(x = year, y = people, color = "Give Directions to Stranger")) +
  geom_line(data = homeless_positive_data, aes(x = year, y = people, color = "Give Money to Homeless")) +
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +
  scale_color_manual(values = colors)
```

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Unhappiness vs. No Altruism"
#| label: fig-2

@@

  geom_line(data = happy_negative_data, aes(x = year, y = people, color = "Happiness")) +
  geom_line(data = directions_negative_data, aes(x = year, y = people, color = "Give Directions to Stranger")) +
  geom_line(data = homeless_negative_data, aes(x = year, y = people, color = "Give Money to Homeless")) +
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +
  scale_color_manual(values = colors)
```
## Discussion

>>>>

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Happiness vs Giving Directions to Strangers"
#| label: fig-1

@@

  geom_line(data = happy_positive_data, aes(x = year, y = people, color = "Happiness")) +
  geom_line(data = directions_positive_data, aes(x = year, y = people, color = "Give Directions to Stranger")) +
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +
  scale_color_manual(values = colors)
```

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Happiness vs Giving Money to Homeless"
#| label: fig-2

@@

  geom_line(data = happy_positive_data, aes(x = year, y = people, color = "Happiness")) +
  geom_line(data = homeless_positive_data, aes(x = year, y = people, color = "Give Money to Homeless")) +
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +
  scale_color_manual(values = colors)
```

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Unhappiness vs. Not Giving Directions to Strangers"
#| label: fig-3

  geom_line(data = happy_negative_data, aes(x = year, y = people, color = "Happiness")) +
  geom_line(data = directions_negative_data, aes(x = year, y = people, color = "Give Directions to Stranger")) +
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +
  scale_color_manual(values = colors)
```

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Unhappiness vs. Not Money to Homeless"
#| label: fig-4

  geom_line(data = happy_negative_data, aes(x = year, y = people, color = "Happiness")) +
  geom_line(data = homeless_negative_data, aes(x = year, y = people, color = "Give Money to Homeless")) +
  scale_x_continuous(breaks = c(2002, 2004, 2012, 2014)) +
  scale_color_manual(values = colors)
```
## Discussion
